---
title: "ggplot_hook"
author: "Oscar"
date: "2023-12-26"
output: html_document
---
# Index
Heres a breakdown of what this R Markdown document contains:

* 1. **YAML Header:** This includes metadata like the title and the output format (`html_document`), which is standard for R Markdown documents.

* 2. **Plot Sections:** Each plot has its own section with a title and a code chunk. The code chunk is enclosed in triple backticks with `{r}` to indicate its R code. Options like `echo=TRUE` ensure the code is displayed in the document, and `message=FALSE` suppresses additional messages that might clutter your presentation.

* 3. **Library Calls:** Necessary library calls (`ggplot2` and `dplyr`) are included. For the last plot, `library(dplyr)` is included within the code chunk since `dplyr` functions are used.

* 4. **Code for Plots:** The `ggplot2` code you provided is included within these sections, creating different types of plots with the `penguins` dataset.

When you knit this document in RStudio, it will produce an HTML file with your plots and descriptions, which you can then present to stakeholders.


## Setting up my environment
Notes: setting up my R environment by loading the 'tidyverse' and 'palmer penguins' packages

```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```
## Exploratory analysis
```{r exploring data}
glimpse(penguins)

```
## Plot 1: Points in Purple

```{r plot1, echo=TRUE, message=FALSE}
library(ggplot2)
library(palmerpenguins)
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(color="purple")
```
## Plot 2: Points by Species Shape
```{r}
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(aes(shape=species))

```
## Plot 3: Points Colored and Shaped by Species
```{r}
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(aes(color=species, shape=species)) +
  facet_wrap(~sex)

```
## Plot 4: Points Colored and Shaped by Species, Excluding Missing Sex
```{r}
library(dplyr)
penguins %>%
  drop_na(sex) %>%
  ggplot(aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(aes(color=species, shape=species)) +
  facet_wrap(~sex)

```

